### 2016-01-26 Manuscript/BiologyLetters/response.tex

\item{\textcolor{blue}{ESM 1, p. 5: axis title should be ``Google Scholar matches,'' not ``Google Scholars matches.'' Figure caption should capitalize ``Google Scholar.'' Y-axis and X-axis should be hyphenated.}}
We fixed the typo in the figure and the caption as well as in the code for reproducing this figure.

\item{\textcolor{blue}{ESM 1, p. 6: ``wrong binomial names format'' should be ``incorrectly-formatted binomial names,'' and ``into the correct ones'' should be deleted.
Fixing is assumed to turn incorrect things into correct ones.
Also, the sentence starting the paragraph under ``Selecting the living OTUs'' repeats the exact same thing as this sentence.}}
We modified the sentence to: ``[we] fixed the incorrectly-formatted binomial names (e.g. \textit{H. sapiens} became \textit{Homo sapiens})''.

\item{\textcolor{blue}{ESM 2 seems to be almost completely redundant with Table 1. Is there some more efficient way of dealing with this information?}}

We replaced the Table 1 in the main text with the Table 1 in the ESM 2 (available data without any number of characters threshold - see reviewer 2 comment 1).
We therefore removed ESM 2 and renamed ESM 3 to ESM 2

@@

\end{enumerate}

%%%%%%%%%%%%%%%
% Reviewer 2 (Graham Slater)
%%%%%%%%%%%%%%%

\section{Reviewer 2 (Graham Slater):} % NC: I feel like some of the comments are missing here? TG: I've added the full comments now.
\begin{enumerate}
\item{\textcolor{blue}{The authors state on page 3 lines 82-90 that they avoided matrices with ``few characters'' due to lower probability of overlapping characters with other matrices and so only selected matrices containing >100 characters. First, a lack of overlapping characters doesn’t seem justifiable, at least to my mind, as a reason to exclude a matrix if the ultimate goal is to infer the placement of extinct taxa relative to extant taxa. Antler ramifications, to use the authors' example, are likely to be a very useful character when attempting to resolve relationships among living and extinct artiodactyls, even if they cannot be coded for monotremes. To flip the argument, a matrix of 200 + characters for mysticetes is similarly likely to contain many non-applicable characters from the perspective of talpids. I do understand that the authors are thinking downstream in terms of super matrices for higher level analyses, but smaller matrices are going to be just as relevant for reaching this goal. You don't have much space in the ms I understand, but surely this needs to be addressed?!}}

%TO DO: let's just remove this threshold thingy since I seem to be the only one to be convinced by it ;)...
% NC: Yep that seems sensible
We removed the analysis with a threshold of OTUs with at least 100 characters and replaced it with the analysis without any minimal number of morphological characters.
We replaced <sentence> with <sentence new> in the manuscript; we updated the results of figure 1 and table 1 to contain all living OTUs; we removed the redundant ESM 2 and we updated the figures

\item{\textcolor{blue}{Along these lines, a 100 character limit may seem rational but this is actually, from a practical perspective, very large. molecular matrices of this size would, of course, be laughed at but many of the most robust phylogenetic studies I'm familiar with come in well under this size. I suspect, but cannot be sure, that this partially explains the poor species level coverage the authors find; higher level studies can readily accumulate large numbers of characters because vastly different morphologies are being compared, often using families or genera as exemplars, leading to an abundance of easily defined characters. Species level studies, on the other, are often focused within families or genera to make them more manageable, but here characters are quickly exhausted. To give some random examples that I'm familiar with, Salles (1992) species-level study of Felidae (all species) was based on 44 characters, Wang and Carranza- Casta\~{n}eda's 2008 study of Mephitidae (\textasciitilde50\% of species but all genera) was based on 38 characters, and Bryant et al's 1993 study of Mustelid genera was of 46 characters. These are all important studies, but do not feature here because of the 100 character limit. At the very least I think this results in a downplaying of previous phylogenetic efforts by morphologists in the results. At worst it misrepresents the state of affairs dramatically. Is 100 really the minimum number you want to go with at all phylogenetic scales?}}

%Check why the matrices didn't came up! - Don't justify not doing it by saying it's hard!

% Justification: maybe data non accessible.

@@

\item{\textcolor{blue}{ESM 2 - ``The following section contains supplementary results to the main body: the available data structure using the NTI and the PD metric'' Abbreviations should be introduced when first used, not later as they are here.}}
We changed this to ``using the Net Relatedness Index (NRI) and the Nearest Taxon Index (NTI) metrics''.
\end{enumerate}

We hope we have responded to all these comments appropriately. Please let us know if you require any further information,\\
\bigskip

% Editorial office comments to authors:
% Please ensure that you include; 
% *An author contributions section which fulfils all *four* of our criteria given here https://royalsociety.org/journals/ethics-policies/openness/, including a sentence stating all authors agree to be held accountable for the content therein and approve the final version of the manuscript 
%TG: TO DO: CHECK
% *A funding statement which is the same as that given in ScholarOne
%TG: To modify
% *Please also confirm in your cover letter whether all the figures are your own or whether permission has been obtained for their use
%TG: TO DO (yes)
% *Please upload your original figure files as eps, tiff or jpeg files, rather than PDFs
%TG: TO DO (easy)
% *If you have any images that can be used to promote your article on social media (should this be accepted) please upload them as a supplementary file
%TG: what about the "phylogeny" with the duck and the pig?
% *Please confirm whether your manuscript should be available via open access, as we note that this may be a requirement of your funder.
%TG: TO DO (yes)

%TG: just fix/add all this in this document
%TG: Make sure word limit is kept to 2500 +/- 5%

### 2016-01-26 Manuscript/BiologyLetters/Supplementary/ESM_2.tex
Added sampling effort analysis (need explanations!)

>>>>

\section{Supplementary results - 1}
The following section contains supplementary blalbalbal....

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supp_figure_sampling_effort.pdf}
\caption{Sampling effort across all mammalian orders on the three different taxonomic levels. The \textit{R$^2$} and the slope (\textit{b}) are reported for each linear model.}
\label{Supp_Figure_sampling}
\end{figure}
